Lattices of acyclic pipe dreams

### 2024-11-15 acyclicFacets/draft/latticePipeDreams.tex
comments mistake

\begin{lemma}
\label{lem:rectangleInsertionAlgorithm}
For any~$t, r, c \in [n]$, the free southeast elbows in the rectangle~$[r] \times [c]$ just before step~$t$ of the insertion algorithm form a staircase of length
\[
\# \set{s < t}{\pi(s) \le r \text{ and } \omega^{-1}(\pi(s)) \le c} - \# \set{s < t}{\pi(s) > r \text{ and } \omega^{-1}(\pi(s)) > c}.
\]
\end{lemma}

>>>>

\begin{lemma}
\label{lem:rectangleInsertionAlgorithm}
For any~$t, r, c \in [n]$, the free southeast elbows in the rectangle~$[r] \times [c]$ just before step~$t$ of the insertion algorithm form a staircase of length
\[
\# \set{s < t}{\pi(s) \le r \text{ and } \omega^{-1}(\pi(s)) \le c} - \# \set{s < t}{\pi(s) > r \text{ and } \omega^{-1}(\pi(s)) > c}.
\]
\vincent{
There is a bug here and in the proof. This should be $\max(0, ...)$.
In the proof, we need to argue that as soon as we use the $\max$ (meaning that a pipe that should contribute to~$-1$ contributes to~$0$), we stay at~$0$ (as we cannot insert pipes that contribute to~$1$, because all non-inversions of~$\omega$ are non-inversions of~$\pi$!!
Add Nathan Reading to the acknowledgements for a discussion that made me observe this bug.
}
\end{lemma}
